### 2019-01-04 methods.tex

The current version of SaltProc only allows 100\% separation efficiency for 
either specific elements or groups of elements (e.g. Processing Groups as described in 
Table~\ref{tab:reprocessing_list}) at the end of the specific cycle time. 
This approach works well for fast-removing elements (gases, noble metals, 
protactinium) which should be removed each depletion step. Unfortunately, 
for the elements with longer cycle times (i.e. rare earths should be removed 
every 50 days) this simplified approach leads to oscillatory behavior of all
major parameters. In future releases of SaltProc, this drawback will be eliminated 
by removing elements with longer cycle times using different method: only mass 
fraction (calculated separately for each reprocessing group) will be removed each
 depletion step (e.g. 3 days).

>>>>

The current version of SaltProc only allows 100\% separation efficiency for 
either specific elements or groups of elements (e.g. Processing Groups as described in 
Table~\ref{tab:reprocessing_list}) at the end of the specific cycle time. 
This simplification neglects the reality that the salt spends appreciable time 
out of the core, in the primary loop pipes and the heat exchanger.

This approach works well for fast-removing elements (gases, noble metals, 
protactinium) which should be removed each depletion step. Unfortunately, 
for the elements with longer cycle times (i.e. rare earths should be removed 
every 50 days) this simplified approach leads to oscillatory behavior of all
major parameters. In future releases of SaltProc, this drawback will be eliminated 
by removing elements with longer cycle times using different method: only mass 
fraction (calculated separately for each reprocessing group) will be removed each
 depletion step or batch (e.g. in the current work it was chosen 3 days).
